 

### 2021-01-26 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd
#31
leaf T figure
#6

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment for 5/6 sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in growing season (a) leaf area density, (b) proportion light incidence, (c) proportion sun leaves, and July mean ± 1 standard deviation for (d) maximum photosyntehtically active ratiation (PAR), (e) maximum wind speed, (f) minimum humidity, (g) maximum $T_{air}$, and (h) maximum biological temperature, $T_{bio}$. All variables are normalized relative to the height of the top of the canopy (**DETAILS**) and the conditions at the point of lowest measurement.   ([Issue 2](https://github.com/EcoClimLab/vertical-thermal-review/issues/2) and [issue 20](https://github.com/EcoClimLab/vertical-thermal-review/issues/20)) ](NEON_height_profiles/figures/profile_all.png)

@@

![**Figure `r fig_NEON_differences`. Role of canopy permeability in shaping temperature buffering, from NEON data.** Current placeholder figure is Nidhi's first rough analysis. See [issue 2](https://github.com/EcoClimLab/vertical-thermal-review/issues/2). ](NEON_height_profiles/figures/differences_across_forests_temp.png)

@@

Height-based leaf trait variation in Quercus alba and Quercus velutina showed decrease in lobation with increased height in two tall species, suggesting an adaptation to hydraulic constraints in order to lower evapotranspiration with increasing height by decreasing lobation [@kusiPlasticLeafMorphology2020]. However, @sackHowStrongIntracanopy2006 did not observe trait variation based on height in Quercus spp.

@@

![**Figure `r fig_leaf_T`. Leaf temperature in response to (a) XXX, (b) XXX (key trait or environmental variables).** Examples to be produced based on energy balance model using the tealeaves R package of @muir_tealeaves_2019: https://github.com/EcoClimLab/vertical-thermal-review/issues/6. Current placeholder shows figures from Campbell&Norman.](leaf_energy_balance/C&N_figures.png)

>>>>

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment for 5/6 sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in growing season (a) leaf area density, (b) proportion light incidence, (c) proportion sun leaves, and July mean ± 1 standard deviation for (d) maximum photosyntehtically active ratiation (PAR), (e) maximum wind speed, (f) minimum humidity, (g) maximum $T_{air}$, and (h) maximum biological temperature, $T_{bio}$. All variables are normalized relative to the height of the top of the canopy (**DETAILS**) and the conditions at the point of lowest measurement.   ([issue 20](https://github.com/EcoClimLab/vertical-thermal-review/issues/20)) ](NEON_height_profiles/figures/profile_all.png)

@@

![**Figure `r fig_NEON_differences`. Role of canopy permeability in shaping temperature buffering, from NEON data.** Current placeholder figure is Nidhi's first rough analysis. See [issue 31](https://github.com/EcoClimLab/vertical-thermal-review/issues/31). ](NEON_height_profiles/figures/differences_across_forests_temp.png)

@@

Height-based leaf trait variation in *Quercus alba* and *Quercus velutina* showed decrease in lobation with increased height in two tall species, suggesting an adaptation to hydraulic constraints in order to lower evapotranspiration with increasing height by decreasing lobation [@kusiPlasticLeafMorphology2020]. However, @sackHowStrongIntracanopy2006 did not observe trait variation based on height in Quercus spp.

@@

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the elevation of $T_{leaf}$ above $T_{air}$ in response to stomatal conductance ($g_s$), wind speed, and shortwave radiation.** Schematic produced using the tealeaves R package of @muir_tealeaves_2019. Current placeholder uses typical conditions for Harvard Forest, but model output deviates from real data (directions right, but Tleaf-Tair too high). [ISSUE #6](2020_12_draft).](leaf_energy_balance/2020_12_draft.png)
